Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-08 paper.tex
update cyclus fundamentals paper reference

One of the major motivations for the development of the Cyclus fuel cycle
simulator \cite{cyclus_2015} was creating a simulation environment that is
more expressive than more traditional fuel cycle simulators.  Cyclus was
designed with a plug-in style architecture that allows different models for
facility types, known as \emph{archetypes}, to be swapped in and out easily.
While the reactor archetypes used in this analysis do not implement
internal physics calculations, plug-in archetypes such as Bright-lite
\cite{flanagan_bright-lite_2014} have been developed for Cyclus that provide
varying degrees modeling fidelity.
% response to technical comment 2.

>>>>

One of the major motivations for the development of the Cyclus fuel cycle
simulator \cite{cyclus-fundamentals-2016} was creating a simulation environment that is
more expressive than more traditional fuel cycle simulators.  Cyclus was
designed with a plug-in style architecture that allows different models for
facility types, known as \emph{archetypes}, to be swapped in and out easily.
While the reactor archetypes used in this analysis do not implement
internal physics calculations, plug-in archetypes such as Bright-lite
\cite{flanagan_bright-lite_2014} have been developed for Cyclus that provide
varying degrees modeling fidelity.
% response to technical comment 2.
